---
title: "p8105_hw6_wm2460"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelr)
library(patchwork)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1
```{r message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


## Problem 2

### Tidying the dataset
```{r message=FALSE}
homicides_df = read_csv("./data/homicide-data.csv")

homicides_new = homicides_df %>% 
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, state, sep = "_")) %>% 
  filter(!city_state %in% c("Dallas_TX", "Phoenix_AZ", "Kansas City_MO", "Tulsa_AL"), 
         victim_race %in% c("Black", "White")) %>% 
  mutate(victim_age = as.numeric(victim_age),
         resolved = as.numeric(disposition == "Closed by arrest"),
         victim_race = fct_relevel(victim_race, "White"),
         victim_sex = fct_relevel(victim_sex, "Female"))

```

### `glm` for Baltimore

```{r glm_baltimore}
baltimore_glm = homicides_new %>% 
  filter(city_state == "Baltimore_MD") %>% 
  glm(resolved ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) %>% 
  broom::tidy()

baltimore_glm

# save the output of glm as an R object
baltimore_glm = homicides_new %>% 
  filter(city_state == "Baltimore_MD") %>% 
  glm(resolved ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) %>% 
  saveRDS(., "./data/Baltimore_glm.rds")
```

### Odds ratio for Baltimore

```{r or_baltimore}
#cannot knit this code chunk
#baltimore_glm %>% 
#  mutate(OR = exp(estimate)) %>%
#  select(term, log_OR = estimate, OR, p.value) %>% 
#  knitr::kable(digits = 3)

```

### `glm` for all cities
```{r glm_all}
#Draft code
#all_glm = homicides_new %>% 
#  nest(all_cities = c(resolved, victim_age, victim_sex, victim_race)) %>%
#  select(city_state, all_cities) %>% 
#  group_by(city_state) %>% 
#  mutate(models = map(.x = all_cities, ~glm(resolved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())),
#         results = map(models, broom::tidy))#
```


## Problem 3

### Load and clearn
```{r p3_load}
bw_df = read_csv("./data/birthweight.csv")

bw_new = bw_df %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace)) %>% 
  drop_na()
```

### Model 1
```{r m1}
m1 = lm(bwt ~ wtgain, data = bw_new)

m1_df = bw_new %>% 
  select(bwt, wtgain) %>% 
  modelr::add_residuals(m1) %>% 
  modelr::add_predictions(m1)

m1_df %>% 
  ggplot(aes(x = wtgain, y = resid)) + geom_violin()
```

I picked the variable `wtgain` as the predictor for model 1 and I picked it based on a hypothesized structure for the factors that underly birthweight. 

The residual plot shows that the residual of `wtgain` is normally distributed following the central limit theorem. 

## Model 2 & 3
```{r m2}
m2 = lm(bwt ~ blength + gaweeks, data = bw_new)

m3 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = bw_new)
```

## Crossvalidation
```{r cv}

```

